Highlighting Disputed Claims on the Web

### 2009-10-29 papers/www_disputefinder/disputefinder.tex
Reorganized content to merge related work into the main paper flow - but haven't yet edited anything

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{trush@berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust. Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims. If a user clicks on a highlighted phrase then Dispute Finder will show the user a summary of articles that support other points of view.

@@

Performing these tasks well is a hard problem, and we do not yet claim to have an implementation that is good enough to be compelling for most users. We do however believe that Dispute Finder attacks an interesting problem that, if addressed well, could significantly improve the utility of the web.

@@

\section{INTRODUCTION}

@@

\section{Related Work}

Dispute Finder builds on prior work in many different areas. The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information. Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}. Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.

\todo{Add more references from the NewsCube paper}

@@

\section{The Dispute Finder System}

Users interact with Dispute Finder in two ways. {\it Skeptical Readers} browse the web using the Dispute Finder Firefox extension and discover when pages they read make disputed claims. {\it Activists} tell Dispute Finder about disputed claims that they care about, add evidence to support their point of view, and help teach Dispute Finder to recognize particular claims on the web.

\subsection{Highlighting Snippets}

\subsection{Explaining Disputed Claims}

\subsection{Trustworthy Sources}

\subsection{What is Disputed?}

@@

\subsection{Finding Snippets}

@@

>>>>

\author{
\alignauthor Rob Ennals\\
       \affaddr{Intel Labs Berkeley}\\
       \affaddr{2150 Shattuck Ave}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{robert.ennals@intel.com}
\alignauthor Beth Trushkowsky\\
       \affaddr{Computer Science Division}\\
       \affaddr{University of California at Berkeley}\\
       \affaddr{Berkeley, CA, USA}\\
       \email{trush@cs.berkeley.edu}
\alignauthor John Mark Agosta\\
       \affaddr{Intel Labs Santa Clara}\\
       \affaddr{2200 Mission College Blvd}\\
       \affaddr{Santa Clara, CA, USA}\\
       \email{john.m.agosta@intel.com}
}

@@

We describe Dispute Finder, a browser extension that alerts a user when information they read online is disputed by a source that they might trust. Dispute Finder examines the text on the page that the user is browsing and highlights any phrases that appear to entail claims in its database of known disputed claims. If a user clicks on a highlighted phrase then Dispute Finder shows them a summary of articles that support other points of view.

@@

In this paper, we explain the design of Dispute Finder, and the trade-offs between the various design decisions that we explored.

@@

\section{Introduction}

@@

%\section{Related Work}
%
%Dispute Finder builds on prior work in many different areas. The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information. Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}. Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.
%
%\todo{Add more references from the NewsCube paper}

\section{Trusting Online Content}

@@

\section{What is Disputed?}

@@

\section{Finding Snippets}

@@

\todo{Talk about this work in the introduction?}

\section{Explaining Disputed Claims}

\subsection{Argumentation Graphs}

\section{Trustworthy Sources}

\section{Highlighting Snippets}
